A Blockchain Consensus Protocol With\\Horizontal Scalability

### 2018-04-23 conference-presentation/presentation.tex
Prepare conference presentation

\setbeamertemplate{navigation symbols}{} % remove navigation symbols
\mode<presentation>{\usetheme{tud}}

@@

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\E}{\mathcal{E}}

@@

% \setbeameroption{show notes}

@@

\author{K.~Cong}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Delft University of Technology] % (optional, but mostly needed)
{
  Faculty of Electrical Engineering, Mathematics and Computer Science\\
  Delft University of Technology}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

% \date{Conference Name, 2013}
\date{August 31, 2017}

@@

\begin{frame}{The dangers of centralisation:~Examples}
  \begin{itemize}
    \item Facebook can predict your opinions and desires from your ``likes''~\cite{youyou2015computer},
      and then create a ``psychographic'' profile for use in political campaigns~\cite{psychographic}
    \item Baidu's promoted search result on medical care caused death of a student~\cite{weizexi}
  \end{itemize}
  \note{
    \begin{itemize}
      \item The treatment was phased out at clinical stage in the US because the success rate is too low
      \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
      completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
      answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
      Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
      with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
      of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
      outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
      words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
      predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
      \item The student had cancer---(synovial sarcoma)
      \item Summary: we live in an age where companies and governments are able to control our thoughts,
      where is the freedom and liberty in that?
    \end{itemize}
  }
\end{frame}

\begin{frame}{Blockchain:~a new hope?}
  \begin{itemize}
    \item Blockchains are distributed (replicated) ledgers with no central control\footnote{In practice, some central control exist.}
    \item They enable internet-scale consensus for the first time
    \item Some initial applications include:
    \begin{itemize}
      \item Digital cash (e.g., Bitcoin, Litecoin)
      \item Domain name system (e.g., Namecoin)
      \item Storage rental (e.g., Filecoin)
      \item General purpose (e.g., Ethereum)
    \end{itemize}
  \end{itemize}
  \note{
    \begin{itemize}
      \item Explain blockchain systems---consensus
    \end{itemize}
  }
\end{frame}

@@

\subsection{Related work}
\begin{frame}{Related work}
  \begin{table}[htb]
    \centering
    \caption{Summary of the scalability properties of many blockchain systems.}
    \label{tab:scalability}
    \begin{tabular}{|l|l|l|l|}
    \hline
    \textbf{\thead{Not\\scalable}} & \textbf{\thead{Somewhat\\scalable}} & \textbf{\thead{Limited horizontal\\scalability}} & \textbf{\thead{True horizontal\\scalability}} \\ \hline
    Bitcoin  & Hyperledger & Elastico          & \textsc{Checo} (this work) \\
    Litecoin & ByzCoin     & OmniLedger        &                \\
    \hline
    \end{tabular}
\end{table}
\begin{center}
\Large{
$\xrightarrow{\qquad\text{scalability}\qquad}$
}
\end{center}
\end{frame}

% \begin{frame}{Related work}
%   State-of-the-art: Sharding
%   \begin{itemize}
%   \item Split state into multiple shards
%   \item Shards run consensus algorithm in parallel
%   \item Difficult to perform atomic inter-shard transactions
%     \begin{itemize}
%       \item Elastico: not possible
%       \item OmniLedger: via Atomic Commit protocol
%     \end{itemize}
%   \item Additional complexity
%   \item Diminishing return
%   \end{itemize}
% \end{frame}

>>>>

@@

\newcommand{\A}{\mathcal{A}}
\renewcommand{\C}{\mathcal{C}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\E}{\mathcal{E}}

@@

\setbeameroption{show notes}

@@

% \author{Kelong Cong \inst{1} \and Zhijie Ren \inst{2} \and Johan~Pouwelse \inst{2}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

% \institute{\inst{1} EPFL \and \inst{2} TU Delft}

\author[Short Name (U ABC)]{%
  \texorpdfstring{%
    \begin{columns}
      \column{.3333\linewidth}
      \centering
      Kelong~Cong \\ \small kelong.cong@epfl.ch \\ EPFL
      \column{.3333\linewidth}
      \centering
      Zhijie~Ren \\ \small z.ren@tudelft.nl \\ TU Delft
      \column{.3333\linewidth}
      \centering
      Johan~Pouwelse \\ \small peer2peer@gmail.com \\ TU Delft
    \end{columns}
 }
 {Author 1, Author 2, Author 3}
}

% \date{Conference Name, 2013}
\date{IFIP Networking, 2018}

@@

% \begin{frame}{The dangers of centralisation:~Examples}
%   \begin{itemize}
%     \item Facebook can predict your opinions and desires from your ``likes''~\cite{youyou2015computer},
%       and then create a ``psychographic'' profile for use in political campaigns~\cite{psychographic}
%     \item Baidu's promoted search result on medical care caused death of a student~\cite{weizexi}
%   \end{itemize}
%   \note{
%     \begin{itemize}
%       \item The treatment was phased out at clinical stage in the US because the success rate is too low
%       \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
%       completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
%       answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
%       Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
%       with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
%       of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
%       outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
%       words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
%       predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
%       \item The student had cancer---(synovial sarcoma)
%       \item Summary: we live in an age where companies and governments are able to control our thoughts,
%       where is the freedom and liberty in that?
%     \end{itemize}
%   }
% \end{frame}

\begin{frame}{Blockchain:~a new hope?}
  \begin{itemize}
    \item Blockchains are distributed (replicated) ledgers with no central control
    \item They enable internet-scale consensus for the first time
    \item Some initial applications include:
    \begin{itemize}
      \item Digital cash (e.g., Bitcoin, Litecoin)
      \item Domain name system (e.g., Namecoin)
      \item Storage rental (e.g., Filecoin)
      \item General purpose (e.g., Ethereum)
    \end{itemize}
  \end{itemize}
  \note{
    \begin{itemize}
      \item Explain blockchain systems---consensus
    \end{itemize}
  }
\end{frame}

@@

\subsection{Related work}
\begin{frame}{Related work}
    \begin{itemize}
        \item Off-chain solution
            \begin{itemize}
                \item Lightning Network
                \item Perun
            \end{itemize}
        \item On-chain solution
            \begin{itemize}
                \item Parameter tuning
                \item BFT consensus (e.g. Tendermint, ByzCoin)
                \item Sharding (e.g. Elastico, OmniLedger)
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Related work}
  State-of-the-art---Sharding:
  \begin{itemize}
  \item Split state into multiple shards
  \item Shards run consensus algorithm in parallel
  \end{itemize}
  Challenges:
  \begin{itemize}
      \item Choosing and evolving the shard size
      \item Perform atomic inter-shard transactions
      \item Parameter choice highly depends on the application
  \end{itemize}
\end{frame}
